experDesign: helping performing experiments on batches

### 2021-04-14 paper.Rmd
Fix typo
Fix references

-   *minDiff*, on [github](https://github.com/m-Py/minDiff), and its successor *anticlust*, on [CRAN](https://cran.r-project.org/package=anticlust), [@usingan] divides the samples into similar groups, ensuring similarity by enforcing heterogeneity within group. Conceptually it is similar to reversing the clustering methods k-means and cluster editing.

@@

*experDesign* also provides several small utilities to make it easier design the experiment in batches. For instance, it helps to calculate the samples to dictribute on the minimum number of batches required with `sizes_batches`.

>>>>

-   *minDiff*, on [github](https://github.com/m-Py/minDiff), and its successor *anticlust*, on [CRAN](https://cran.r-project.org/package=anticlust), divides the samples into similar groups, ensuring similarity by enforcing heterogeneity within group [@papenberg].
    Conceptually it is similar to reversing the clustering methods k-means and cluster editing.

@@

*experDesign* also provides several small utilities to make it easier design the experiment in batches.
For instance, it helps to calculate the samples to distribute on the minimum number of batches required with `sizes_batches`.
